Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-01-28 content.tex
Described nLTT statistic (too?) briefly, fix #80

The fourth step quantifies the inference error made. 
First the burn-in fraction is removed, i.e. the first phase of the 
Markov chain Monte Carlo (MCMC) run,
which samples an unrepresentative part of state space. 
By default, \verb;pirouette; 
removes the first 10\% of the posterior.
From the remaining posterior \verb;pirouette; 
creates an error distribution, by measuring the difference
between the true tree and each of the posterior 
trees (Fig.~\ref{fig:pipeline}, 4a $\rightarrow$ 5a).
The default way to quantify the difference between two phylogenies
is the nLTT statistic (\cite{janzen2015approximate}), but any 
user-defined error statistic can be used.

>>>>

The fourth step quantifies the inference error made. 
First the burn-in fraction is removed, i.e. the first phase of the 
Markov chain Monte Carlo (MCMC) run,
which samples an unrepresentative part of state space. 
By default, \verb;pirouette; 
removes the first 10\% of the posterior.
From the remaining posterior \verb;pirouette; 
creates an error distribution, by measuring the difference
between the true tree and each of the posterior 
trees (Fig.~\ref{fig:pipeline}, 4a $\rightarrow$ 5a).
The user can specify a function to quantify the differences between
the true and posterior trees. By default, the package uses the nLTT 
statistic (\cite{janzen2015approximate}), which is the absolute difference
between the normalized lineages-through-time plots of two trees.
